Deployable Probabilistic Programming

### 2019-04-21 paper/paper.tex
case studies in progress

%\linespread{1.0}

@@

// Observe implements the Model interface.The
// parameter vector is lambda, observations.
func (dist expon) Observe(x []float64)
	float64 {
	lambda, y := x[0], x[1:]
	if len(y) == 1 {
		return dist.Logp(lambda, y[0])
	} else {
		return dist.Logps(lambda, y...)
	}
}

@@

// Logps computes the log pdf of a vector
// of observations.
func (_ expon) Logps(lambda float64, y ...float64)
	float64 {
	ll := 0.
	logl := math.Log(lambda)
	for i := range y {
		ll += logl - lambda*y[i]
	}
	return ll
}
	\end{lstlisting}
	\caption{Exponential distribution in Infergo.}
	\label{fig:exponential-distribution}
\end{figure}

@@

\subsection{8 schools}

@@

  return ll
}
\end{lstlisting}
\centering
b. Infergo
	\end{minipage}
	\caption{8 schools: Stan vs. Infergo. The Go implementation
	has a similar length and structure to the Stan model.}
	\label{fig:8-schools}
\end{figure*}

\subsection{Linear regression}

@@

\subsection{Gaussian mixture}

>>>>

\linespread{1.1}

@@

// Observe implements the Model interface. The
// parameter vector is lambda, observations.
func (dist expon) Observe(x []float64)
	float64 {
	lambda, y := x[0], x[1:]
	if len(y) == 1 {
		return dist.Logp(lambda, y[0])
	} else {
		return dist.Logps(lambda, y...)
	}
}

@@

// Logps computes the log pdf of a vector
// of observations.
func (_ expon) Logps(lambda float64, y ...float64)
	float64 {
	ll := 0.
	logl := math.Log(lambda)
	for i := range y {
		ll += logl - lambda*y[i]
	}
	return ll
}
	\end{lstlisting}
	\caption{The exponential distribution in Infergo.}
	\label{fig:exponential-distribution}
\end{figure}

@@

In this section, we present three case studies of probabilistic
programs, each addressing a different aspect of Infergo. Eight
schools (Section~\ref{sec:8-schools}) is a popular example  we
use to compare model specification in Stan and Infergo. Linear
regression (Session~\ref{sec:8-schools}) formulated as a
probabilistic program lets us explore a model comprising
multiple methods and illustrate the inference-simulation use
case. Gaussian mixture (Section~\ref{sec:gaussian-mixture}) is
the most complex model of the three, featuring nested loops and
dynamic control structure.

By no means the models presented in this section reflect 
complexity or the size of real-world Infergo applications, the
latter reaching hundreds of lines of code in length and
performing inference on tens of thousands of data entries.
Rather, their purpose is to provide a general picture of 
probabilistic programming with Infergo.

\subsection{Eight schools}
\label{sec:8-schools}

The eight schools problem~\cite{GCS+03}

@@

  return ll
}
\end{lstlisting}
\centering
b. Infergo
	\end{minipage}
	\caption{Eight schools: Stan vs. Infergo. The Go implementation
	has a similar length and structure to the Stan model.}
	\label{fig:8-schools}
\end{figure*}

\subsection{Linear regression}
\label{sec:linear-regression}

@@

\subsection{Gaussian mixture}
\label{sec:gaussian-mixture}
